---
title: "Homework_02"
author: "brennastallings"
date: "9/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)of AN597 for Modules 6&7.

Question 1

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

P(x; λ) = (e-λ) (λx) / x!
λ=15
e = 2.71828

What is the probability that she will hear more than 8 calls during any given session?

```{r echo=FALSE}
##this is a cumulative poisson distribution where x>=8
#dpois(x>8, lambda=15)
##This gives me a set of values, so NOPE
#1-sum(dpois(x>8, lambda=15))
#THis may be right, not sure, the probability seems high

#These 2 are wrong
```

```{r}
ppois(q=7, lambda = 15, lower.tail = FALSE)
#q is 7, because with lower.tail=FALSE, the P[X > x], so to include 8, q=7

```

What is the probability that she will hear no calls in a session?
```{r}
##probabilty where x=0
dpois(x=0, lambda=15)
```


What is the probability that she will hear exactly 3 calls in a session?
```{r}
##probability where x=3
dpois(x=3, lambda=15)
```


Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r}
x <- 0:30
l = 15
probset<-dpois(x=x,lambda=l)
barplot(probset,names.arg=x,space=0,xlab="x",ylab="Pr(X = x)",main="Probability Mass Function")
```


Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
```{r echo=FALSE}
#x <- 0:30
x<-c(0:30)
l = 15
probset<-dpois(x=c(1:30),lambda=l)
#gives the probabilty of each # in the vector 1:30
ncall<-104

#Saturdays <- function(x) {
#  sample(1:30, x, replace=TRUE)
##not sure I can sample from Probset
#  }
#twoyear<-Saturdays(ncall)
##the above code doesnt take the probabilities into account, but gives out the right sort of output
```

```{r}
x<-c(0:30)
l = 15
probset<-dpois(x=c(1:30),lambda=l)
#gives the probabilty of each # in the vector 1:30
ncall<-104
Saturdays <- function(x) {
  sample(1:30, x, replace=TRUE, prob = probset)
#not sure I can sample from Probset
  }
twoyear<-Saturdays(ncall)

#prob= tells the fxn to find the probability of each of the #s 1:30 in the vector called probset

```


Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30.
```{r echo=FALSE}
hist(twoyear, probability=TRUE, main="Sample Calls", xlab="Number of Calls", ylab="Probability", xlim=c(0,30))

```


#How does your histogram compare to the shape of the probability mass function you plotted above?

The shape is not as symmetrical as the original. It tends to be skewed to one side.
```{r echo=FALSE}
x<-c(0:30)
l = 15
probset<-dpois(x=c(1:30),lambda=l)
ncall<-100000
Saturdays <- function(x) {
  sample(1:30, x, replace=TRUE, prob = probset)
  }
twoyear<-Saturdays(ncall)

hist(twoyear, probability=TRUE, main="Sample Calls", xlab="Number of Calls", ylab="Probability", xlim=c(0,30))
##This was unnecessary, I just wanted to see what would happen if you sampled more times
```
>5 Challenges

1. I tried to use the dpois function when I needed to use the ppois function

2. I thought that I had a functioning code for the first question but it was only because I hadnt cleared out the environment so it was using variables I didnt actually have defined.

3. I couldnt get the code for the final question to work. My graph wasnt properly taking the probabilites from the Poisson into account.

4. I was having the final function sample from the probabilities from the Poisson instead of the numbers in it.

5. I cannot get the bins in my final graph to match the bins in the mass function that we had made before.