---
title: "Homework_02"
author: "brennastallings"
date: "9/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)of AN597 for Modules 6&7.

Question 1

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

P(x; μ) = (e-μ) (μx) / x!
μ=15
e = 2.71828

What is the probability that she will hear more than 8 calls during any given session?
First put in reasoning, written out(dont need to follow naming conventions outside of chunks)
```{r}
##this is a cumulative poisson distribution where x>=8

```

What is the probability that she will hear no calls in a session?
```{r}
##probabilty where x=0

```


What is the probability that she will hear exactly 3 calls in a session?
```{r}
##probability where x=3
```


Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r}

```


Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
```{r}

```


Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30.
```{r}

```


How does your histogram compare to the shape of the probability mass function you plotted above?